Measurement of the \ce{^{64}Zn},\ce{^{47}Ti}(n,p) Cross Sections using a DD Neutron Generator for Medical Isotope Studies

### 2017-08-07 First_np_Paper/arXiv/first_np_paper.tex
Edited version after co-author feedback on reviewer comments.  Resubmitting this revised manuscript to NIM

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
% \usepackage{microtype}
% \usepackage{listings}
% \usepackage{mcode}
\usepackage{csquotess}
% \usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}

@@

Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
 While reactors produce copious quantities of neutrons, their energy spectra is often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
 Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides. DT generators may also often be limited by the restricted use of tritium at many institutions.

@@

The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community. 
 The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a}.
 The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
 In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.

The present work features a pair of cross section measurements for the production of two non-standard positron emitters: \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.

@@

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
This generator extracts deuterium ions from an RF-heated deuterium plasma through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
A 100 kV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.

% \begin{figure}
%  \centering
% %  \includegraphics[width=\columnwidth]{IMG_20160531_183154957_HDR.jpg}
%  \includegraphics[scale=0.06]{IMG_20160531_183154957_HDR.jpg}
%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
%  \label{fig:alt_HFNG}
% \end{figure}

% \begin{figure*}
%     \centering
%     \begin{subfigure}[t]{0.4\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{Capture.PNG}
%         \includegraphics[height=3in]{Capture.PNG}
%         \caption{The UC Berkeley High-Flux Neutron Generator,}
%         \label{fig:hfng_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.4\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[height=2in]{target2.png}
%         \caption{Cutaway of the target chamber.}
%                 \label{fig:hfng_b}
%     \end{subfigure}
%     \caption{Note: the ion source is approximately 20 cm in diameter.}
%      \label{fig:main_HFNG}
% \end{figure*}

\begin{figure}
    \centering
        \centering
%         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[height=2in]{target2.png}
        \includegraphics[height=2in]{cutaway.png}
        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
                \label{fig:hfng_b}
%      \label{fig:main_HFNG}
\end{figure}

@@

\begin{figure}
    \centering
%         \includegraphics[width=\columnwidth]{Capture.PNG}
        \includegraphics[height=2.5in]{holder.pdf}
        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
        \label{fig:holder_a}
\end{figure}

% \begin{figure*}
%     \centering
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{Capture.PNG}
%         \includegraphics[height=2in]{foils.png}
%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
%         \label{fig:holder_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[height=2in]{holder.pdf}
%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
%                 \label{fig:holder_b}
%     \end{subfigure}
%      ~ 
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[height=2in]{IMG_20151103_113432563.jpg}
%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
%                 \label{fig:holder_c}
%     \end{subfigure}
%     \caption{}
%      \label{fig:main_holders}
% \end{figure*}

@@

% \begin{table*}
% \centering
% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
% }
% \label{tab:foil_specs}
% \resizebox{\textwidth}{!}{%
% \begin{tabular}{ccccccc}
% \toprule
% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \minitab[c]{Foil Density \\ (mg/cm$^2$)} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g)                                                                                    \\ \midrule
% 
% 
% 
% 
% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}0.49 \pm 0.02* \\ 0.50 \pm 0.03* \\ 0.49 \pm 0.03* \\ 0.53 \pm 0.06$^\dagger$ \\ 0.50 \pm 0.02$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}9.75 \pm 0.09* \\ 9.98 \pm 0.15* \\ 9.96 \pm 0.10* \\ 10.01 \pm 0.11$^\dagger$ \\ 10.00 \pm 0.09$^\dagger$\end{tabular} & \begin{tabular}{S[table-format=+1.3,
%    table-figures-uncertainty=1]}0.248 \pm 0.005* \\ 0.248 \pm 0.005* \\ 0.241 \pm 0.005* \\ 0.247 \pm 0.005$^\dagger$\\  0.248 \pm 0.005$^\dagger$\ \end{tabular} \\ \hline
%    
%    
%    
% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}1.03 \pm 0.01 \\ 1.03 \pm 0.01 \\ 1.02 \pm 0.01\end{tabular}                                    & \begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}9.93 \pm 0.14 \\ 9.76 \pm 0.17 \\ 9.89 \pm 0.15\end{tabular}                                     & \begin{tabular}{S[table-format=+1.3,
%    table-figures-uncertainty=1]}0.538 \pm 0.005 \\ 0.451 \pm 0.005 \\ 0.452 \pm 0.005\ \end{tabular}                           \\ \hline
% 
% 
% 
% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}1.16 \pm 0.02 \\ 1.15 \pm 0.02\end{tabular}                                                         &\begin{tabular}{S[table-format=+1.2,
%    table-figures-uncertainty=1]}9.93 \pm 0.04 \\ 9.94 \pm 0.03\end{tabular}                                                          & \begin{tabular}{S[table-format=+1.3,
%    table-figures-uncertainty=1]}0.337 \pm 0.005 \\ 0.337 \pm 0.005\ \end{tabular}                                   \\ \bottomrule
% \end{tabular}%
% }
% \end{table*}

% \begin{table*}
% \centering
% \caption{Foil characteristics for each of the three (Zn/In)* experiments and the two (Ti/In)$^\dagger$  experiments.
% }
% \label{tab:foil_specs}
% \resizebox{\textwidth}{!}{%
% \begin{tabular}{@{}ccccccc@{}}
% \toprule
% Foils Used & Metal Purity          & Abundance (a/o)                                                           & \begin{tabular}[c]{@{}c@{}}Foil Density \\ (mg/cm$^2$)\end{tabular} & Thickness (mm)                                                                                                         & Diameter (mm)                                                                                                           & Mass (g, $\pm$ 5 mg)                                                                                    \\ \midrule
% $^\text{nat}$In      & \textgreater 99.999\% & \begin{tabular}[c]{@{}c@{}}\ce{^{113}In} (4.29\%),\\ \ce{^{115}In} (95.71\%)\end{tabular} & 365.5                                                            & \begin{tabular}[c]{@{}c@{}}0.49 $\pm$ 0.02*, \\ 0.50 $\pm$ 0.03*, \\ 0.49 $\pm$ 0.03*, \\ 0.53 $\pm$ 0.06$^\dagger$, \\ 0.50 $\pm$ 0.02$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}9.75 $\pm$ 0.09*, \\ 9.98 $\pm$ 0.15*, \\ 9.96 $\pm$ 0.10*, \\ 10.01 $\pm$ 0.11$^\dagger$, \\ 10.00 $\pm$ 0.09$^\dagger$\end{tabular} & \begin{tabular}[c]{@{}c@{}}0.248*, \\ 0.248*, \\ 0.241*, \\ 0.247$^\dagger$,\\  0.248$^\dagger$\ \end{tabular} \\ \hline
% $^\text{nat}$Zn      & \textgreater 99.99\%  & \ce{^{64}Zn} (49.17\%)                                                            & 714.1                                                            & \begin{tabular}[c]{@{}c@{}}1.03 $\pm$ 0.01, \\ 1.03 $\pm$ 0.01, \\ 1.02 $\pm$ 0.01\end{tabular}                                    & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.14, \\ 9.76 $\pm$ 0.17, \\ 9.89 $\pm$ 0.15\end{tabular}                                     & \begin{tabular}[c]{@{}c@{}}0.538, \\ 0.451, \\ 0.452\ \end{tabular}                           \\ \hline
% $^\text{nat}$Ti      & 99.999\%              & \ce{^{47}Ti} (7.44\%)                                                             & 450.6                                                            & \begin{tabular}[c]{@{}c@{}}1.16 $\pm$ 0.02, \\ 1.15 $\pm$ 0.02\end{tabular}                                                         & \begin{tabular}[c]{@{}c@{}}9.93 $\pm$ 0.04, \\ 9.94 $\pm$ 0.03\end{tabular}                                                          & \begin{tabular}[c]{@{}c@{}}0.337, \\ 0.337\ \end{tabular}                                   \\ \bottomrule
% \end{tabular}%
% }
% \end{table*}

% \comment{Need foil data from Mauricio's 2nd Ti run}

@@

% \begin{figure}
%  \centering
%  %trim option's parameter order: left bottom right top
%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{mcnp_vised2.png}
%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
%  \label{fig:mcnp_vised}
% \end{figure}

@@

The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
The neutron spectral distribution is also broadened by the temperature of the target.  
This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
This spectrum, peaked around 2.75 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.

@@

% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{mcnp_flux.pdf}
%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
%  \label{fig:mcnp_flux}
% \end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{mcnp_flux_new.pdf}
 % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
 \caption{MCNP6-modeled neutron energy spectrum for the HFNG.  The solid lines show the spectrum at the location of the indium and the target foil respectively. The dotted and dashed lines show the same with the target itself \enquote{voided} to remove scattering contributions.  Less than 1\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.}
 \label{fig:mcnp_flux}
\end{figure}

@@

While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
Due to the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:

@@

% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{fracplot.pdf}
%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
%  \label{fig:frac_plot}
% \end{figure}

@@

% \begin{figure*}[H]
%     \centering
%     \begin{subfigure}[t]{0.7\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{Capture.PNG}
%         \includegraphics[height=2.8in]{IMG_20160531_182618557_HDR.jpg}
%         \caption{ Ortec 80\% HPGe detector}
%         \label{fig:hpge_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.28\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[height=2.8in]{IMG_20160531_182635712_HDR.jpg}
%         \caption{Ortec planar LEPS detector}
%                 \label{fig:hpge_b}
%     \end{subfigure}
%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
%      \label{fig:main_ge_detectors}
% \end{figure*}
% 
% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{Capture.PNG}
%         \includegraphics[width=5in]{ti_foils.png}
        \subfigimg[width=5in]{a)}{47sc_gspectrum_alt.pdf}
%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
% 	\caption{}
        \refstepcounter{subfigure}\label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{target2.png}
%         \includegraphics[width=5in]{Sample_spectra.png}
        \subfigimg[width=5in]{b)}{64Cu_gspectrum_alt.pdf}
%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
          \refstepcounter{subfigure}       \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production. (a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
     \label{fig:main_spectra}
\end{figure*}

@@

If the target is subjected this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:

>>>>

\usepackage{xfrac}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
% \usepackage{cool}
% \usepackage{cancel}
\usepackage{microtype}
% \usepackage{listings}
% \usepackage{mcode}
\usepackage{csquotess}
% \usepackage{longtable}
\usepackage{subcaption}
\usepackage{booktabs,siunitx}
\usepackage{gensymb}
\usepackage[normalem]{ulem}

@@

Two other potential neutron sources for (n,x) reactions exist in addition to the secondary neutron fields generated at existing isotope production facilities: reactors and neutron generators that utilize the D(T,n)$\alpha$ (\enquote{DT}) and D(D,n)\ce{^3He} (\enquote{DD}) reactions.
 While reactors produce copious quantities of neutrons, their energy spectra are often not well-suited to the preparation of high-purity samples due to the co-production of unwanted activities via neutron capture, in addition to the significant start-up costs and proliferation concerns involved in their commissioning \cite{Updegraff2013}.
 Similarly, while the higher energy 14-15 MeV neutrons produced at DT generators are capable of initiating (n,p) and (n,$\alpha$) reactions, their higher energy opens the possibility of creating unwanted activities via (n,pxn) and (n,$\alpha$xn) reactions that cannot easily be separated from the desired radionuclides. DT generators may also often be limited by the restricted use of tritium at many institutions.

@@

The purpose of the present work is to explore the potential to use high-flux neutron generators to produce high-specific activity samples of radionuclides at the mCi level for local use in the application community. 
 The research group at UC Berkeley has  developed a High Flux Neutron Generator (HFNG) that features an internal target where samples can be placed just several millimeters from the neutron producing surface in order to maximize the utilization of the neutron yield for the production of a desired radionuclide \cite{Waltz2017,Waltz2016a,doi:10.1063/1.3267832}.
 The HFNG uses the D(D,n)\ce{^3He} reaction to produce neutrons with energies near 2.45 MeV together with a self-loading target design to maintain continuous operation without target replacement.
 In addition to the generator itself, efforts are underway to design neutron reflection capabilities to allow scattered neutrons multiple opportunities to interact with an  internally mounted target.
While these design efforts are underway, the HFNG can be used to better characterize production cross sections at the appropriate neutron energy.

The present work features a pair of cross section measurements for the production of two emerging non-standard medical radionuclides: the positron emitter \ce{^{64}Zn}(n,p)\ce{^{64}Cu} and the single - photon emission computed tomography (SPECT) tracer \ce{^{47}Ti}(n,p)\ce{^{47}Sc}.
\ce{^{64}Cu}  ($t_{1/2}$ = 12.7 h) undergoes $\beta^+$ decay (61.5\% branching ratio) to \ce{^{64}Ni} or $\beta^-$ decay (38.5\% branching ratio) to \ce{^{64}Zn} \cite{Singh2007}.
The emitted short-range 190-keV $\beta^-$ particle makes this an  attractive  therapeutic radionuclide, which also has the possibility for simultaneous positron emission tomography (PET) imaging for real-time dose monitoring and verification.
This makes \ce{^{64}Cu} particularly desirable  for emerging radiation therapy protocols \cite{Lewis2003,NSACIsotopesSubcommittee2015,Bandari2014,mp500671j}.
In addition, copper radiochemistry is well developed, and many existing ligands and carriers may be used for selective delivery of the radionuclide to different sites in patients.
The second radionuclide studied, \ce{^{47}Sc} ($t_{1/2}$ = 3.35 d), undergoes $\beta^-$ decay to \ce{^{47}Ti}, emitting a high-intensity (63.8\%) 159-keV gamma ray in the process \cite{Burrows2007}.
This radionuclide is  attractive as an emerging diagnostic isotope, due to the similarity of the emitted gamma ray to that of the  well-established \ce{^{99m}Tc} \cite{Qaim2011,Qaim201731,Kolsky1998,mausner1995evaluation}.
Due to the short half-life ($t_{1/2}$ = 6.0 h) of and dwindling supplies of \ce{^{99m}Tc}, \ce{^{47}Sc} stands poised as a potential solution to this shortage, due to its longer half-life and multiple production pathways without the need for highly enriched uranium \cite{Browne2011}.
In addition, when paired with \ce{^{44}Sc}, \ce{^{47}Sc} forms a promising \enquote{theranostic} pair for use in simultaneous therapeutic and diagnostic applications \cite{Muller2014,Deilami-nezhad2016}.

@@

Neutron activation was carried out via irradiation in the High-Flux Neutron Generator (HFNG), a DD neutron generator at the University of California, Berkeley.
This generator extracts deuterium ions from an RF-heated deuterium plasma (using ion sources similar to  designs from the Lawrence Berkeley National Laboratory \cite{doi:10.1063/1.3267832}) through a nozzle, whose shape was designed to form a flat-profile beam, 5 mm in diameter.
This deuterium beam is incident upon a water-cooled, self-loading titanium-coated copper target \cite{Waltz2017,Waltz2016a}, where the titanium layer acts as a reaction surface for DD fusion, producing neutrons with a well-known energy distribution as a function of  emission angle \cite{Liskien_Paulsen_1973}.
While the machine's design features two deuterium ion sources impinging from both sides of the target, only a single source was used in the present work.
Irradiation targets are inserted in the center of the titanium layer deuteron target, approximately 8 mm from the DD reaction surface, prior to startup.
\autoref{fig:hfng_b} displays a cut-away schematic of the HFNG.
A 100 keV deuterium beam was extracted at 1.3 mA, creating a flux of approximately  $\sci{1.3}{7}$ neutrons/cm$^2$s on the target.

% \begin{figure}
%  \centering
% %  \includegraphics[width=\columnwidth]{./figures/IMG_20160531_183154957_HDR.jpg}
%  \includegraphics[scale=0.06]{./figures/IMG_20160531_183154957_HDR.jpg}
%  % IMG_20160531_183154957_HDR.jpg: 2432x4320 pixel, 72dpi, 85.80x152.40 cm, bb=0 0 2432 4320
%  \caption{Alternate HFNG picture - \color{red}{use this or  \autoref{fig:hfng_a}?}}
%  \label{fig:alt_HFNG}
% \end{figure}

% \begin{figure*}
%     \centering
%     \begin{subfigure}[t]{0.4\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[height=3in]{./figures/Capture.PNG}
%         \caption{The UC Berkeley High-Flux Neutron Generator,}
%         \label{fig:hfng_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.4\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2in]{./figures/target2.png}
%         \caption{Cutaway of the target chamber.}
%                 \label{fig:hfng_b}
%     \end{subfigure}
%     \caption{Note: the ion source is approximately 20 cm in diameter.}
%      \label{fig:main_HFNG}
% \end{figure*}

\begin{figure}
    \centering
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2in]{./figures/target2.png}
        \includegraphics[height=2in]{cutaway.png}
        \caption{Cut-away schematic of the HFNG. The ion source is approximately 20 cm in diameter.}
                \label{fig:hfng_b}
%      \label{fig:main_HFNG}
\end{figure}

@@

\begin{figure}
    \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
        \includegraphics[height=2.5in]{holder.pdf}
        \caption{Schematic (not drawn to scale) of the sample holder used for the Berkeley HFNG,}
        \label{fig:holder_a}
\end{figure}

% \begin{figure*}
%     \centering
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[height=2in]{./figures/foils.png}
%         \caption{Schematic (not drawn to scale) of the foil co-loading holder for the Berkeley HFNG,}
%         \label{fig:holder_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2in]{./figures/holder.pdf}
%         \caption{\color{red}{Use this or \autoref{fig:holder_a} - which is more appropriate?}}
%                 \label{fig:holder_b}
%     \end{subfigure}
%      ~ 
%     \begin{subfigure}[t]{0.3\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2in]{./figures/IMG_20151103_113432563.jpg}
%         \caption{ zinc (visible) foil co-loaded on top of reference indium foil, ready for irradiation.}
%                 \label{fig:holder_c}
%     \end{subfigure}
%     \caption{}
%      \label{fig:main_holders}
% \end{figure*}

@@

@@

% \begin{figure}
%  \centering
%  %trim option's parameter order: left bottom right top
%  \includegraphics[trim = 0mm 0mm 2mm 0mm, clip,width=\columnwidth]{./figures/mcnp_vised2.png}
%  % mcnp_vised2.PNG.png: 688x443 pixel, 96dpi, 18.21x11.72 cm, bb=0 0 516 332
%  \caption{MCNP6 model of the HFNG target chamber, with reference scale. The co-loaded foils can be seen in the target chamber center.  The ovals indicate the location of water cooling channels.}
%  \label{fig:mcnp_vised}
% \end{figure}

@@

The Monte Carlo N-Particle transport code  MCNP6 \cite{goorley2013initial} was used to model the neutron energy spectrum incident upon target foils co-loaded into the HFNG (see \autoref{fig:mcnp_flux}).
The neutron spectral distribution is also broadened by the temperature of the target.  
This gives rise to a slight difference in the neutron energy at the target location \cite{Waltz2016a}, which has been included in our stated energy window.
This spectrum, peaked around 2.777 MeV, illustrates the forward-focused kinematics of the DD reaction subtended by the co-loaded sample foils.
 As expected, the  production target is the dominant source of scatter - approximately 0.78\%  of the neutrons incident on the foils can be attributed to scatter in the neutron production target.

@@

% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{./figures/mcnp_flux.pdf}
%  % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
%  \caption{MCNP6-modeled neutron energy spectrum for the Berkeley HFNG, using co-loaded indium and zinc (for \ce{^{64}Cu} production) foils as an example.}
%  \label{fig:mcnp_flux}
% \end{figure}

\begin{figure}
 \centering
 \includegraphics[scale=0.6]{mcnp_flux_new.pdf}
 % mcnp_flux.pdf: 373x295 pixel, 72dpi, 13.16x10.41 cm, bb=0 0 373 295
 \caption{MCNP6-modeled neutron energy spectrum for the HFNG.  The solid lines show the spectrum at the location of the indium and the activation foil. The dotted and dashed lines show the same with the neutron production target itself \enquote{voided} to remove scattering contributions.  }
 \label{fig:mcnp_flux}
\end{figure}

@@

While this shows that the sample foils experience a very narrow energy distribution of incident neutrons, an effective neutron energy window must be determined.
The MCNP6 simulation shows an identical flux-weighted average neutron energy of 2.765 MeV for both the Indium and target foils to the 1 keV level.
Due to geometry and the kinematics of DD neutron emission, $E_{max}$,  the maximum energy of a neutron subtending the target foils in this geometry is 2.783 MeV \cite{Liskien_Paulsen_1973}.
For this maximum energy, the number of reactions induced in a foil (containing $N_T$ target nuclei) is given by:

@@

% \begin{figure}
%  \centering
%  \includegraphics[scale=0.6]{./figures/fracplot.pdf}
%  % fracplot.pdf: 372x295 pixel, 72dpi, 13.12x10.41 cm, bb=0 0 372 295
%  \caption{Fraction of total reactions induced in the Indium foil between the energies [0, $E'$]}
%  \label{fig:frac_plot}
% \end{figure}

@@

% \begin{figure*}[H]
%     \centering
%     \begin{subfigure}[t]{0.7\textwidth}
%         \centering
% %         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182618557_HDR.jpg}
%         \caption{ Ortec 80\% HPGe detector}
%         \label{fig:hpge_a}
%     \end{subfigure}%
%     ~ 
%     \begin{subfigure}[t]{0.28\textwidth}
%         \centering
% %         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[height=2.8in]{./figures/IMG_20160531_182635712_HDR.jpg}
%         \caption{Ortec planar LEPS detector}
%                 \label{fig:hpge_b}
%     \end{subfigure}
%     \caption{High-Purity Germanium Detectors used for gamma spectroscopy of the activated foils.}
%      \label{fig:main_ge_detectors}
% \end{figure*}
% 
% \comment{Does \autoref{fig:main_ge_detectors} serve any purpose? Should it be cut?}

@@

\begin{figure*}[ht]
    \centering
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\columnwidth]{./figures/Capture.PNG}
%         \includegraphics[width=5in]{./figures/ti_foils.png}
        \subfigimg[width=5in]{a)}{./47sc_gspectrum_alt.pdf}
%         \caption{ Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector}
% 	\caption{}
        \refstepcounter{subfigure}\label{fig:spectra_a}
    \end{subfigure}%
    \\
    \begin{subfigure}[t]{\textwidth}
        \centering
%         \includegraphics[width=\textwidth]{./figures/target2.png}
%         \includegraphics[width=5in]{./figures/Sample_spectra.png}
        \subfigimg[width=5in]{b)}{./64Cu_gspectrum_alt.pdf}
%         \caption{Gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
          \refstepcounter{subfigure}       \label{fig:spectra_b}
    \end{subfigure}
    \caption{Example gamma spectra collected to monitor radioisotope production. (a)  Gamma spectrum for the \ce{^{47}Ti}(n,p)\ce{^{47}Sc} production pathway foils, counted using a LEPS detector and (b) gamma spectrum for the \ce{^{64}Zn}(n,p)\ce{^{64}Cu} production pathway foils, counted using an 80\% HPGe detector.}
     \label{fig:main_spectra}
\end{figure*}

@@

If the target is subjected to this flux  for an irradiation  time $t_i$ and decays for a  delay time $t_d$ (after end-of-beam) before gamma ray spectrum acquisition occurs for a counting time  $t_c$, then the number of product decays ($N_D$; with decay constant $\lambda$) during the acquisition will be:
